TBD

### 2021-03-16 outputs/paper/paper.Rmd
S10 regression + table complete
same issues with tables in LaTex as S9, gonna troubleshoot that after completing S9's regression completely.

# Discussion

>>>>

```{r S10, echo = FALSE, warning = FALSE, message = FALSE}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

# UK, Poland, and US
s10_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40)
s10_main$cond <- ifelse(s10_main$cond == 3, 1, 0)

s10_main_result <- lm(response ~ cond, data = s9_main)

# UK
s10_uk <- s9_main %>%
  filter(country == 39)
s10_uk_result <- lm(response ~ cond, data = s10_uk)

# Poland
s10_poland <- s10_main %>%
  filter(country == 27)

s10_poland_result <- lm(response ~ cond, data = s10_poland)

# USA
s10_usa <- s10_main %>%
  filter(country == 40)
s10_usa_result <- lm(response ~ cond, data = s10_usa)

# final table
stargazer(s10_main_result, s10_uk_result, s10_poland_result, s10_usa_result, 
          title = "Reporting rates in Money-No Key condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money-NoKey", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```
# Discussion
